Transparent Standby for Low-Power, Resource-Constrained Embedded Systems

### 2018-02-16 LCTES/body.tex
(+) PM module

spawn async/isr [CEU_ADC_IRQ_N, 0] do
    var int value = <...>; // port with the value read
    emit ANALOG_DONE(value);
end

code AnalogRead (var int pin) -> int do
    {ceu_pm_set(CEU_PM_ANALOG, 1);}
    do finalize with
        {ceu_pm_set(CEU_PM_ANALOG, 0);}
    end

@@

>>>>

async/isr ADC_vect_num do
    var int value = <...>; // port with the value read
    emit ANALOG_DONE(value);
end

code AnalogRead (var int pin) -> int do
    {PM_SET(PM_ANALOG, 1);}
    do finalize with
        {PM_SET(PM_ANALOG, 0);}
    end

@@

\begin{figure}[t]
\begin{lstlisting}[numbers=left]
#define PM_GET(peripheral)       bitRead(pm, peripheral)
#define PM_SET(peripheral,state) bitWrite(pm, peripheral, state);

static u32 pm = 0;

void pm_sleep (void) {
  if (PM_GET(PM_TIMER1) || PM_GET(PM_USART) || PM_GET(PM_SPI)) {
      LowPower.idle(PM_GET(PM_ADC),...)
    } else if (PM_GET(PM_ADC)) {
      LowPower.adcNoiseReduction(...);
    } else {
      LowPower.powerDown(...);
    }
  }
}
\end{lstlisting}
%\rule{8.4cm}{0.37pt}
\caption{ Power management module for the ATmega328p microcontroller.
\label{lst.pm}
}
\end{figure}

### 2018-02-16 LCTES/lctes.tex
(+) PM module

\usepackage{listings}
\lstdefinelanguage{ceu}{%
  language=C,
  morekeywords={%
    and, uint32_t, code,
    await, bool, call, class, data, define, deterministic, do, each, else,
    emit, end, escape, event, every, finalize, hor, implementation, in,
    input, interface, loop, min, native, new, nohold, not, or, output, par,
    pool, pure, return, signal, spawn, tag, then, this, traverse, until,
    var, watching, when, with},
}
\lstset{
  basicstyle=\ttfamily,
  captionpos=b,
  columns=flexible,
  commentstyle=\rmfamily\itshape,
  escapeinside={||},
  frame=tb,
  keepspaces=true,
  keywordstyle=\bfseries,
  language=ceu,
  mathescape=true,
  numbersep=4pt,
  numberstyle=\scriptsize,
  upquote=true,
}

>>>>

\usepackage{listings}
\lstdefinelanguage{ceu}{%
  language=C,
  morekeywords={%
    and, uint32_t, code, async, isr,
    await, bool, call, class, data, define, deterministic, do, each, else,
    emit, end, escape, event, every, finalize, hor, implementation, in,
    input, interface, loop, min, native, new, nohold, not, or, output, par,
    pool, pure, return, signal, spawn, tag, then, this, traverse, until,
    var, watching, when, with},
}
\lstset{
  basicstyle=\ttfamily,
  captionpos=b,
  columns=flexible,
  commentstyle=\rmfamily\itshape,
  escapeinside={||},
  frame=tb,
  keepspaces=true,
  keywordstyle=\bfseries,
  language=ceu,
  mathescape=true,
  numbersep=4pt,
  numberstyle=\scriptsize,
  upquote=true,
}
